Deep Reinforcement Learning for Conservation Decisions

### 2021-06-08 manuscript/manuscript.Rmd
updated
fix gh-actions:
gh-actions cannot use cuda-based image: no space left on device

<!-- Something about the way forward, point to appendix resources etc -->

<!-- Discussion really doesn't discuss/draw conclusions from the fisheries and tipping points examples! Do we need to or maybe not since it's not about the science-->

<!-- ML: I think talking about the examples in a very passing manner is fine as the point is primarily to show that RL can work. To conclude, I feel like we could portray the vision of open ai gym environments building a CS-ecology community.-->

<!-- 
The pitfalls of RL-based solutions to global environmental change problems are not only technical, but include issues of ethics and power, especially when the algorithms or data are proprietary.
We discuss not only technical issues that can cause RL solutions to fail in surprising ways, but also potential issues raised by the adoption of more algorithmic approaches to conservation generally.
We emphasize how an open, transparent and reproducible approach can help mitigate some (but not all) of these concerns, and facilitate a more effective interface between teams of researchers from both ecological and computer sciences.
If algorithms are to play a meaningful role in the allocation and exploitation of natural resources from fish to forests, good intentions [@Joppa] may not be sufficient to ensure equitable outcomes.
Ecologists and computer scientists will also need input from experts in governance and ethics to ensure that applications of AI to ecological challenges are fair and just.

>>>>

\pagebreak

# References
